Self-interacting dark matter model without dark energy in cosmology

### 2024-12-26 article/article.tex
pictures from eps to pdf qso use the newly params

\documentclass[twocolumn]{aastex631}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\graphicspath{{./pictures/}}

@@

   To constrain the relevant IDM models (\cite{refId0}), we use the newly revised
   observational $H(z)$ data (OHD)(\cite{PhysRevD.71.123001};
   \cite{Daniel.Stern_2010};\cite{M.Moresco_2012};\cite{Zhang_2014};
   \cite{Moresco_2016};\cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037};
   \cite{Borghi_2022};\cite{Jiao_2023}),the Pantheon+ set of 1701 SNe Ia 
   (\cite{Scolnic_2022}), the QSO data from \cite{Lusso_2020}, 
   the BAO data from SDSS and DESI 2024, and the reduced CMB parameters
   from Planck 2018.

@@

   We use the fiducial SN Ia magnitude ($M_b$) determined from SH0ES 2021 Cepheid 
   host distances(\cite{Riess_2022}), which gives the $\mu_{\text{data}}$ and we 
   give the $\chi^2$ as 
   \begin{equation}
      \chi_{\text{SNe}}^2=\Delta^{\text{T}}C^{-1}\Delta,
   \end{equation}
   where $\Delta=(\mu_{\text{th}}-\mu_{\text{data}})$ and $C^{-1}$ is the inverse of the
   covariance matrix of the SNe Ia data, the distance modulus is $\mu=5\log_{10}(d_L/\text{Mpc})+25$, and the
   luminosity distance $d_L$ can be given as a function of redshift $z$
   \begin{equation}
      d_L=(1+z)\int_0^z\frac{c\mathrm{d}z'}{H(z')}.\label{eq:15}
   \end{equation}
   To eliminate the advanced restriction to $H_0$ from $M_b$, we adopt
   the likelihood function as
   \begin{equation}
      \widetilde{\chi}_{\text{SNe}}^2=A-\frac{B^2}{C}+\ln\left(\frac{C}{2\pi}\right),
   \end{equation}
   where $A=\Delta^{\text{T}}C^{-1}\Delta,B=\Delta^{\text{T}}C^{-1}$ and $C$ is the sum of $C^{-1}$.
   Apparently these two functions give the same constraints in $\Omega_{2,0}$ and
   $\log_{10}(\kappa C_1)$

@@

\subsection{Reduced CMB parameters}

   We used the reduced CMB parameters $\{l_A,R,z_{*}\}$ from Planck 2018
   to constrains the model. The reduced CMB parameters are
   \begin{equation}
      l_A=\frac{\pi r(z_{*})}{r_s(z_{*})}
   \end{equation}
   which refer to acoustic scale, and the shift parameter is given as
   \begin{equation}
      R=H_0\sqrt{\Omega_{m0}}r(z_{*})\sim H_0\sqrt{\Omega_{2,0}}r(z_{*}),
   \end{equation}
   where $r(z_{*})$ and $r_s(z_{*})$ are defined as
   \begin{eqnarray}
      r(z_{*})=\int_0^{z_{*}}\frac{z'\mathrm{d}z'}{H(z')},\\
      r_s(z_{*})=\int_{z_{*}}^{\infty}\frac{c_s\mathrm{d}z'}{H(z')}.
   \end{eqnarray}
   As the same as what we do in BAO data, we choose the cross parameter
   $r_s(z_{*})h$ and give the $z_{*}\simeq1090$ to constrain the model.

@@

@@

   The Eq.(\ref{eq:8}) convergant to the flat ΛCDM model as
   $\log_{10}(\kappa C_1)\to-\infty$, therefore the constraints
   could only give the upper limit of what, and give the lower limit
   of $M_x$, respectively.

   \begin{figure}[htbp]
      \centering
   \end{figure}

>>>>

\documentclass[twocolumn]{aastex631}
\usepackage{subfigure}
\graphicspath{{./pictures/}}

@@

   To constrain the relevant IDM models (\cite{refId0}), we use the newly revised
   observational $H(z)$ data (OHD)(\cite{PhysRevD.71.123001};
   \cite{Daniel.Stern_2010};\cite{M.Moresco_2012};\cite{Zhang_2014};
   \cite{Moresco_2016};\cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037};
   \cite{Borghi_2022};\cite{Jiao_2023}),the Pantheon+ set of 1701 SNe Ia 
   (\cite{Scolnic_2022}), the QSO data from \cite{Lusso_2020}, 
   the BAO data from SDSS and DESI 2024.

@@

   We use the fiducial SN Ia magnitude ($M_b$) determined from SH0ES 2021 Cepheid 
   host distances(\cite{Riess_2022}), which gives the $\mu_{\text{data}}$ and we 
   give the $\chi^2$ as 
   \begin{equation}
      \chi_{\text{SNe}}^2=\Delta^{\text{T}}C^{-1}\Delta,
   \end{equation}
   where $\Delta=(\mu_{\text{th}}-\mu_{\text{data}})$ and $C^{-1}$ is the inverse of the
   covariance matrix of the SNe Ia data, the distance modulus is $\mu=5\log_{10}(d_L/\text{Mpc})+25$, and the
   luminosity distance $d_L$ can be given as a function of redshift $z$
   \begin{equation}
      d_L=(1+z)\int_0^z\frac{c\mathrm{d}z'}{H(z')}.\label{eq:15}
   \end{equation}
   To eliminate the advanced restriction to $H_0$ from $M_b$, we adopt
   the likelihood function as
   \begin{equation}
      \widetilde{\chi}_{\text{SNe}}^2=\chi_{\text{SNe}}^2-\frac{B^2}{C}+\ln\left(\frac{C}{2\pi}\right),
   \end{equation}
   where $B=\Delta^{\text{T}}C^{-1}$ and $C$ is the sum of $C^{-1}$.
   Apparently these two functions give the same constraints in $\Omega_{2,0}$ and
   $\log_{10}(\kappa C_1)$.

@@

@@

   The prior range set for free parameters are given at Table \ref{tab:4}

   \begin{table}[htbp]
      \caption{Parameters and priors used in analysis}
      \centering
      \begin{tabular}{lll}
         \hline\hline
         parameter & initial & prior \\
         \hline
         $\Omega_{2,0}$ & 0.3 & $\mathcal{U}[0.0,1.0]$ \\
         $n$ & --- & $\mathcal{U}[-10,10]$ \\
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & --- & $\mathcal{U}[-10,0]$ \\
         $H_0$[km/s/Mpc] & 70 & $\mathcal{U}[60,80]$ \\
         \hline
         $r_{\text{d}}h$[Mpc] & 100 & $\mathcal{U}[50,150]$ \\
         \hline
         $\beta$ & $-11$ & $\mathcal{U}[-15,-5]$ \\
         $\gamma$ & 0.6 & $\mathcal{U}[0.0,1.0]$ \\
         $\delta$ & 0.2 & $\mathcal{U}[0.0,1.0]$ \\
         \hline
      \end{tabular}
      \label{tab:4}
   \end{table}

@@

   The Eq.(\ref{eq:8}) convergant to the flat ΛCDM model as
   $\log_{10}(\kappa C_1)\to-\infty$, therefore the constraints
   could only give the upper limit of what, and give the lower limit
   of $M_x$ according to Eq.(\ref{eq:9}), respectively.

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{ohd_2.pdf}
      }
      \caption{The constraint result from the observational
      $H(z)$ data}
   \end{figure}

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{sne_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{sne_2.pdf}
      }
      \caption{The constraint result from the supernovae
      Ia data}
   \end{figure}

   \begin{figure}[htbp]
      \centering
      \subfigure{
         \includegraphics[width=0.22\textwidth]{bao_1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.22\textwidth]{bao_2.pdf}
      }
      \caption{The constraint result from the BAO data}
   \end{figure}
